%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font

%------------------------------------------------

\name{Woodson Miles} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{woodson.miles@my.wheaton.edu \\ 731.796.5288} % Main address

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{Kellogg, Brown, \& Root}{July 2024 - Present}{Cloud Engineer}{Colorado Springs, CO}
		\item Vivamus PostgreSQL fermentum semper porta. Nunc diam velit PHP, adipiscing ut tristique vitae
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Lockheed Martin}{June 2021 - July 2024}{DevSecOps Engineer}{Colorado Springs, CO}
		\item Provided tier 3 DevOps support for software team of 70+ engineers.
		\item Automated product delivery, improving deployment stability by 30\% for a \$10 million web app.
		\item Planned curriculum for and taught LM’s Secure Coding class
		\item Received a 2023 Extraordinary Engineering and Technology Award (EETA) for student mentorship.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Lockheed Martin}{June 2021 - July 2024}{Full Stack Software Engineer}{Colorado Springs, CO}
		\item Designed a web app saving over \$20,000/quarter in part manufacturing downtime.
		\item Authored the Lockheed Martin (LM) Space Corporate Functional Aid for Secure Software Development.
		\item Led surge effort to integrate API services, accelerating delivery schedule by five months on the LM Capability Catalog.
		\item Distinguished as LM Space Recognized Technical Talent (RTT) 2022.
		\item Performed at the “Significantly Exceeds” level (highest rating) every year since start.
		\item Developed a web app that reduces Risk Management Framework (RMF) labor by 20\% for a \$1.7 billion program.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Colorado Army National Guard Cyber}{Sep 2018 - Dec 2023}{Deputy Team Chief}{Colorado Springs, CO}
		\item Defended the 2021 state elections from foreign interference as leader of the cyber support team by threat hunting for adversaries targeting ballet systems.
		\item Mobilized the cyber task force in response to cyber attacks against state infrastructure.
		\item Evaluated joint defense teams in Cyber Shield, the longest running and largest Department of Defense unclassified cyber exercise
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Lockheed Martin}{June 2017 - July 2021}{Cyber Security Engineer}{Colorado Springs, CO}
		\item Developed a vulnerability tool that saved \$10,000/year in cyber security labor for a \$2 billion program.
		\item Received a 2018 EETA for cyber innovation.
		\item Led development for award-winning cyber app that saved \$80,000/year in cyber security labor for a \$2 billion program.
		\item Led GPS Control System (GCS) vulnerability tests using STIG, ACAS, and SCAP.
		\item Owned and delivered timely GCS assessment plans and vulnerability reports to decision makers.
	\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	\textbf{Wheaton College, Wheaton, IL} \hfill \textit{May 2017} \\ 
	B.S. in Computer Science \& Math Minor \\
	Math Minor \\
	Summa cum laude \\
	GPA: 3.85
	
\end{rSection}

\begin{rSection}{Active \& Former Certifications}

	\textbf TS/SCI Security Clearance with CI Polygraph, Certified Information System Security Professional (CISSP),  GIAC Cloud Security Essentials (GCLD), Certified Ethical Hacker, Security+, Cisco Certified Network Associate

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
		Protocols \& APIs & XML, JSON, SOAP, REST \\
		Databases & MySQL, PostgreSQL, Microsoft SQL \\
		Tools & SVN, Vim, Emacs
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
